bbox
====

```{r echo=FALSE}
knitr::opts_chunk$set(
  comment = "#>",
  collapse = TRUE,
  warning = FALSE,
  message = FALSE
)
```

[![Build Status](https://travis-ci.org/ropensci/bbox.svg?branch=master)](https://travis-ci.org/ropensci/bbox)
[![codecov](https://codecov.io/gh/ropensci/bbox/branch/master/graph/badge.svg)](https://codecov.io/gh/ropensci/bbox)

`bbox` gets bounding boxes

Various interfaces:

* Input long/lat and value to make a polyogn, then get the bbox, using either
    * `sp`/`rgeos`, or
    * GeoJSON via `lawn`
* Input Spatial objects (`sp` package) and spit out the bbox
* Input GeoJSON data and spit out the bbox
* Input Well Know Text data and spit out the bbox
* Input Simple Features (`sf` package) data and spit out the bbox


## Installation

```{r eval=FALSE}
remotes::("ropensci/bbox")
```

```{r}
library("bbox")
```

## lon/lat to bbox

```{r}
lonlat2bbox(lon=-120, lat=45, width=10^4)
```

## get bbox from any spatial object

```{r}
library(sf)
nc <- st_read(system.file("shape/nc.shp", package="sf"))
b_box(nc)
```

## Meta

* Please [report any issues or bugs](https://github.com/ropensci/bbox/issues).
* License: MIT
* Get citation information for `bbox` in R doing `citation(package = 'bbox')`
* Please note that this project is released with a [Contributor Code of Conduct](CODE_OF_CONDUCT.md).
By participating in this project you agree to abide by its terms.
